Process_OlisJazEmData

### 2024-02-26 Code/Process_OlisJazEmData.Rmd
Removed 1 MED4, red light , 30 uE from PUR calculation as it did not grow, skewed PUR results

OlisJazMetaPUR <- OlisJazMetaPUR %>%
  group_by(Strain, WL, Par_ue) %>% 
  mutate(Pur_ue = round(mean(CalcPur_ue)),
         PurParRatio = (Pur_ue / Par_ue))%>% 
ungroup()  %>% 
  select(-c(CalcPur_ue))

>>>>

OlisJazMetaPUR <- OlisJazMetaPUR %>%
  filter(SampleID != "MiSa1364") %>% 
  group_by(Strain, WL, Par_ue) %>% 
  mutate(Pur_ue = round(mean(CalcPur_ue)),
         PurParRatio = (Pur_ue / Par_ue))%>% 
ungroup()  %>% 
  select(-c(CalcPur_ue))
